Naturalness in U(1) extensions of the MSSM

### 2014-12-19 paper/e6ssm-tuning-paper.tex
Added temporary comment

Interestingly the coefficient $d$ is very small (and negative) in the
case of the $U(1)_I$.  This allows a dramatic reduction in the fine
tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$
charge associated with $U(1)_I$ vansihing, which means that the
D-terms to the lightest Higgs which is predominantly $H_u$ at large
$\tan \beta$ are suppressed, making it difficult to raise the Higgs
mass in the same way as happens in the other models, explaining why
the heavier Higgs values are less well populated [can't be obtained? -
are we sure those scattered points are valid?]  than in the other
models.  Therefore the fine tuining behaviour in this model is closer
to that of the MSSM, though the LHC can still constrain the most
natural scenarions from just placing tougher limits on the $Z^\prime$
mass .

>>>>

Interestingly the coefficient $d$ is very small (and negative) in the
case of the $U(1)_I$.  This allows a dramatic reduction in the fine
tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$
charge associated with $U(1)_I$ vansihing, which means that the
D-terms to the lightest Higgs which is predominantly $H_u$ at large
$\tan \beta$ are suppressed, making it difficult to raise the Higgs
mass in the same way as happens in the other models, explaining why
% DH:: I strongly suspect that they are invalid - but running scan
% to check this currently
the heavier Higgs values are less well populated [can't be obtained? -
are we sure those scattered points are valid?]  than in the other
models.  Therefore the fine tuining behaviour in this model is closer
to that of the MSSM, though the LHC can still constrain the most
natural scenarions from just placing tougher limits on the $Z^\prime$
mass .
